Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-06 ms.tex
conclusions 2

\item Galaxies with $10^{6}M_{\odot} \lesssim \Mbh \lesssim 10^8
  \Msun$ with star formation histories matching the average values
  derived from the cosmological simulations of
  \citet{MosterNaab+:2013a} possess an effective heating rate $v_w\sim
  1000$ km s$^{-1}$, relatively independent of SMBH mass
  (Fig.~\ref{fig:vwSources}).  This results in a prediction for the
  average Eddington ratio $\eddr \propto \Mbh^{\alpha}$ with
  $\alpha\lsim 0.5 \, (0.8)$ for core (cusp) galaxies which is tension
  with the trend of measured nuclear X-ray luminosities of early-type
  galaxies (e.g., \citealt{Miller+15}), which instead find that
  $\eddr$ increases towards smaller $\Mbh$.  However, high X-ray
  radiative efficiencies are required for these galaxies to be
  consistent with thermally-stable accretion, instead suggesting that
  (at least at low black hole masses), the possibility of two branches
  of accretion states.

>>>>

\item The nuclei of galaxies with relatively low mass black holes, $10^{6}M_{\odot} \lesssim \Mbh \lesssim 10^8
  \Msun$, and star formation histories which match their average value derived from the cosmological simulations, receive a stellar wind heating rate $v_w\sim 800$ km s$^{-1}$, relatively independent of SMBH mass (Fig.~\ref{fig:vwSources}).  This predicts an average Eddington ratio that increases weakly with $M_{\bullet}$, in mild tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type
  galaxies (e.g., \citealt{Miller+15}).

For thermally-stable models, scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude can result from from (1) stochastic variation in star formation history from galaxy to galaxy; (2) Variations in small scale outflow rates due to variations between galactic nuclear angular momenta.

However, only for relatively high X-ray radiative efficiencies do distant galaxies with measured X-ray luminosities accretion rates low enough to be consistent with thermally-stable accretion.  The possibility that high mass quiescent BHs may in fact occupy a thermally-unstable state is excacerbated by the deep potential wells of these galaxies relative to the wind heating.  If the current sample , this may suggest a separate "thermally stable" branch (at least for low mass BHs).   t
